---
title: "Getting to Know infer"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    df_print: default
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(tidyverse)
library(infer)
tutorial_options(exercise.timelimit = 60,
                 exercise.checker = gradethis::grade_learnr)
```

## Welcome

In this tutorial, you will learn how to use the `infer` R package to conduct hypothesis tests on tidy data. Rather than providing methods for specific statistical tests, this package consolidates the principles that are shared among common hypothesis tests into a set of 4 main verbs (functions), supplemented with many utilities to visualize and extract value from their outputs.

### The 4 Main Verbs

The workflow of this package is designed around four main verbs. Starting out with some dataset,

+ `specify()` allows you to specify the variable, or relationship between variables, that you're interested in.
+ `hypothesize()` allows you to declare the null hypothesis.
+ `generate()` allows you to generate data reflecting the null hypothesis.
+ `calculate()` allows you to calculate a distribution of statistics from the generated data to form the null distribution.


### The `gss` dataframe

Throughout this tutorial, we'll make use of the `gss` dataset supplied by `infer`, containing a sample of 3000 observations of 11 variables from the *General Social Survey*. Print the `gss` dataset to check it out!

```{r gss, exercise = TRUE}
# check out the `gss` dataset
```

<div id="gss-hint">
**Hint:** Type `gss` and then click the Submit Answer button.
</div>

```{r gss-solution}
gss
```

```{r gss-check}
gradethis::grade_code(gradethis::random_praise())
```



